When are Fuzzy Extractors Possible?

### 2015-02-11 trunk/info-bounds/FuzzyExtPossibility-crypto.tex

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of that ball, the number of points cannot be
too high and there will be entropy left after the sketch is published.
%
This remaining entropy is sufficient for extracting a key.

>>>>

\paragraph{Techniques for Positive Results for a Precisely Known
  Distribution} 
We now explain how to construct a secure sketch for a precisely known
distribution $W$ with fuzzy min-entropy (we already explained how to
construct a fuzzy extractor from it).  We begin with distributions in
which all points in the support have the same probability (so-called
``flat'' distributions).  Consider some subsequent reading $w'$. To
achieve correctness, the sketch algorithm must disambiguate which
point $w\in W$ within distance $t$ of $w'$ was
sketched. Disambiguating multiple points can be accomplished by
universal hashing, as long as the size of hash output space is
slightly greater than the number of possible points. Thus, our sketch
is computed via a universal hash of $w$. To determine the length of
that sketch, consider the heaviest (according to $W$) ball $B^*$ of radius
$t$. Because the distribution is flat, $B^*$ is also the ball with the
most points of nonzero probability. Thus, the length of the sketch
needs to be slightly greater than the logarithm of the number of
non-zero probability point in $B^*$. Since $\Hfuzz(W)$ is
determined by the weight of $B^*$, the number of points cannot be
too high and there will be entropy left after the sketch is published.
%
This remaining entropy is sufficient for extracting a key.
